Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-07-31 talk/vmil2012/paper.tex
set preprint option
refine point

\documentclass[10pt]{sigplanconf}

@@

\todo{add page numbers (draft) for review}
In this paper we describe and analyze how deoptimization works in the context
of tracing just-in-time compilers. What instructions are used in the
intermediate and low-level representation of the JIT instructions and how these
are implemented.

@@

As in previous sections the underlying idea for the design of guards is to have
a fast on-trace profile and a potentially slow one in the bail-out case where
the execution takes one of the side exits due to a guard failure. At the same
time the data stored in the backend needed to rebuild the state needs to be as
compact as possible to reduce the memory overhead produced by the large number
of guards, the numbers in Figure~\ref{fig:backend_data} illustrate that the
compressed encoding currently has about 25\% of the size of of the generated
instructions on x86.

>>>>

\documentclass[10pt,preprint]{sigplanconf}

@@

In this paper we describe and analyze how deoptimization works in the context
of tracing just-in-time compilers. What instructions are used in the
intermediate and low-level representation of the JIT instructions and how these
are implemented.

@@

As in previous sections the underlying idea for the design of guards is to have
a fast on-trace profile and a potentially slow one in the bail-out case where
the execution takes one of the side exits due to a guard failure. At the same
time the data stored in the backend needed to rebuild the state needs to be as
compact as possible to reduce the memory overhead produced by the large number
of guards, the numbers in Figure~\ref{fig:backend_data} illustrate that the
compressed encoding currently has about 15\% to 25\% of the size of of the
generated instructions on x86.
